---
title: "Honours Lecture Practical"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---



## Honours Lecture Practical

Objectives: Rough idea of

- What R is and how it works
- What simulation studies are and how they work

## Small Print / Assumptions Two sample t-test

1. Normality: Errors are normally distributed
(robust unless n very small)
1. Homogeneity of Variances: Variances of errors are equal across groups $\sigma_1^2=\sigma^2_2$.
(robust unless group sizes unequal $n_\text{max} \ n_\text{min} > 1.5$)
1. Idependence: Errors are indepdent from each other
(not robust)

## We are skeptical!

Research questions:

1.  $t$-test valid when the assumptions are met?
1. What happens when the assumptions are violated?

## Plan

Create artifical data and check what happens

Recap defintion $95\%$ confidence interval estimator:

- Math: $\mathbb{P}(\theta^* \in \delta(D))=95\%$
- English: The true parameter is within $95\%$ of the generated intervals

--> Generate many intervals (data sets) and check

## Detailed Plan / Pseduocode

- Repeat often (Repeat)
  1. Generate data (Data)
  2. Calculate confidence interval (CI)
  3. Check: True value in confidence interval? (Check)
- Count how often true value is in confidence interval (Count)
 
## Data: Generating Artifical Data
5 Coin tosses from a fair coin
```{r generate data}
coinTosses <- rbinom(5,1,0.5)
print(coinTosses)
```

## Data: Generating Normal Data
```{r generate normal}
set.seed(1903)
group1 <- rnorm(n=10,mean=20,sd=1) 
group2 <- rnorm(n=10,mean=3,sd=1)
print(round(group1,2))
print(round(group2,2))
```

## CI: Performing the $t$-test

```{r t.test}
tResult <- t.test(group1,group2,var.equal=TRUE)
print(tResult)
```

## CI: Extracting the Confidence Interval

```{r extract t.test result}
confInter <- tResult$conf.int
print(confInter)
```

## Check: Check a  value in CI

```{r CI check}
toCheck <- 0
if (toCheck > confInter[1] && toCheck < confInter[2]){
  isIn <- TRUE
}else{
  isIn <- FALSE
}
print(isIn)
```


## Repeat: Repeating a Part
```{r loop}
for (i in 1:3){
  variable <- rnorm(n=1,mean=20,sd=1) 
  print(sprintf('Iteration: %d, Variable %.2f',i,variable))
}
```

## Count: Check + Repeat
```{r loop and check}
tails <- 0
for (i in 1:5){
  coinToss <- rbinom(1,1,0.5)
  if (coinToss==1){
    tails <- tails + 1
  }
}
```

## Pair Exercise

Repeat often (for i in 1:100)

  1. Generate data according to the assumptions (rnorm)
  2. Calculate confidence interval (t.test)
  3. Check and Count: True value in confidence interval? (if ...; count <- count+1)

## Solution

See extra file


## Advanced Function


